prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-05 inst/MyArticle/paper.Rmd
Add bfabric paragraph in Discussion

## plotting panels A-D
pl <- lfqd$get_Plotter()
panelA <- pl$intensity_distribution_density() +
  ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")
panelB <- agr$plot()$plots[[1]] + ggplot2::labs(tag = "B")
panelC <- lfqp$get_Stats()$violin() + ggplot2::labs(tag = "C")
pl <- lfqp$get_Plotter()
panelD <- pl$boxplots()$boxplot[[1]] + ggplot2::labs(tag = "D")
ggpubr::ggarrange(panelA, panelB, panelC, panelD)
```

@@

>>>>

## plot panels A-D
pl <- lfqd$get_Plotter()
panelA <- pl$intensity_distribution_density() +
  ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")
panelB <- agr$plot()$plots[[1]] + ggplot2::labs(tag = "B")
panelC <- lfqp$get_Stats()$violin() + ggplot2::labs(tag = "C")
pl <- lfqp$get_Plotter()
panelD <- pl$boxplots()$boxplot[[1]] + ggplot2::labs(tag = "D")
ggpubr::ggarrange(panelA, panelB, panelC, panelD)
```

@@

To ease the usage barriers of the R package to users not being so familiar with statistics and R programming, we integrated some workflows into our Local Laboratory Information Management System (LIMS) [b-fabric](https://fgcz-bfabric.uzh.ch/) @bfabric.
This integration enables our users to select the input and basic settings in a graphical user interface. As an output, the user receives a report including the R markdown file and all necessary input files to reprocess the analysis on their devices.
In this way, we also support the reproducible science efforts of the community.
